Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-16 demystify.tex
updates

Having an external and major fellowship can significantly improve your chances of getting into a good PhD program (\autoref{sec:fellowships}).  The National Science Foundation Graduate Research Fellowship Program (NSF GRFP) and the Department of Defense National Defense Science and Engineering Graduate Fellowship (DoD NDSEG) are two of the most prestigious fellowships for CS PhD students who are US citizens or permanent residents.  It is rumored that several universities would revert their admission decision on a student if they get one of these fellowships.

@@

The NSF GRFP is a prestigious fellowship for US citizens, nationals, and permanent residents who are in the early stages of their graduate study in STEM fields, including both MS and PhD students. The fellowship provides three years of financial support, which includes a stipend and tuition. The GRFP is highly competitive, with many applicants from top schools, with strong LoRs and research experience.

@@

\item \textbf{Overexaggeration Lors.} Many GRFP applicants are from top schools with well-known professors that are very good at writing. However, they often use flowery language and completely overrate their students. Reviewers are  professors themselves and can sense this overexaggeration.  So you should ask your LoR writers to tone down the language (similar to overclaiming research conributions when writing papers) and and be specific with concrete examples to demonstrate why you're \emph{``the best''}.

@@

The NDSEG is another prestigious fellowship supporting \emph{U.S. citizens} pursuing advanced degrees in STEM fields \emph{critical to national defense} (such as CS).
It provides up to three years of funding, including a  stipend and tuition coverage.

>>>>

Having an external and major fellowship can significantly improve your chances of getting into a good PhD program (\autoref{sec:fellowships}).  The National Science Foundation Graduate Research Fellowship Program (NSF GRFP) and the Department of Defense National Defense Science and Engineering Graduate Fellowship (DoD NDSEG) are two of the most prestigious fellowships for CS PhD students who are US citizens or permanent residents.  
These fellowship provide multiple years of full financial support, which includes a stipend and tuition. 
It is rumored that several programs would revert their admission decision on a student if they get one of these fellowships.

@@

The NSF GRFP is a prestigious fellowship for US citizens, nationals, and permanent residents who are in the early stages of their graduate study in STEM fields, including both MS and PhD students. The GRFP is highly competitive, with many applicants from top schools, with strong LoRs and research experience.

@@

\item \textbf{Overexaggeration Lors.} Many GRFP applicants have LoRs from professors that are very good at writing. However, they often use flowery language and completely overrate their students. Reviewers can sense this overexaggeration and might not trust the LoRs. This is similar to overclaiming research conributions when writing papers. 
So you should mention this to your LoR writers so that they can tone down the language and and be specific with concrete examples to demonstrate why you're \emph{``the best''}.

@@

The NDSEG is another prestigious fellowship supporting \emph{U.S. citizens} pursuing advanced degrees in STEM fields \emph{critical to national defense} (such as CS). NDSEG has several differences from NSF GRFP, e.g., it redacts more information from the reviewers and focuses more on defense-related research.
